Bioverse: Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2024-11-18 src/tex/ms.tex
draft an abstract

\begin{abstract}
    ...
\end{abstract}

>>>>

\begin{abstract}
The origins of life on Earth may provide testable hypotheses about biosignature distributions in exoplanet populations.
Motivated by the cyanosulfidic origins-of-life scenario, we investigate the hypothesis that a minimum past near-ultraviolet (NUV) flux is necessary for abiogenesis.
Using a semi-analytical Bayesian framework und the Bioverse survey simulator, we estimate the probability of obtaining strong evidence for or against this UV Threshold Hypothesis with potential future biosignature surveys.
Our results indicate that a correlation between past NUV flux and current biosignature occurrence is observationally testable, but requires sample sizes of at least 50 planets for meaningful constraints.
These constraints are critically sensitive to the intrinsic abiogenesis rate, as well as host star properties, particularly maximum past NUV fluxes.
Surveys targeting extreme NUV flux values and planets orbiting M dwarfs enhance the likelihood of obtaining conclusive results, with sample sizes $\gtrsim$100 providing $\gtrsim$80\% likelihood of strong evidence if abiogenesis rates are high and required NUV fluxes are moderate. Conversely, the fraction of inhabited planets sharply decreases for required fluxes exceeding a few hundred erg/s/cm².

Our findings demonstrate the potential of upcoming exoplanet surveys to test origins-of-life hypotheses.
 Beyond specific scenarios, our work underscores the broader value of realistic survey simulations in identifying testable science questions, optimizing mission strategies, and advancing theoretical and experimental studies of abiogenesis.
 This approach emphasizes the need to contextualize biosignature detections, enhancing their credibility and offering new approaches to explore the emergence of life on Earth and beyond.
\end{abstract}
